\begin{rSection}
{\small \normalfont \textbf{ TECHNICAL EXPERIENCES \& PROJECTS}}
       
   % PROJECT/TECHNICAL experience entry
    % \begin{rSubsection}{Mexican Train Game, \slshape{Java Project} }{\ttfamily Oct 2023 - Present}{Implementing The Multiplayer Domino-based Game with a GUI in Java}{}
    %     \item Applied object-oriented principles for scalability, integrated JavaFX for user-friendly interface, and conducted JUnit testing for correctness and robustness.
    %     \item Implemented a custom LinkedLists data structure, Lambda expression, and comparator \& iterator interfaces for a streamlined, modular game implementation.
    % \end{rSubsection}

\begin{rSubsection}{\bf \href{https://www.ignasxv.com/Math} {Probabilistic estimation of constants}}
    {\ttfamily Jun 2021 - August 2021}
    {Research Fellowship {\normalfont \small \ttfamily | Python, Sci-Kit learn, Pandas, Jupyter Notebook}}
    {Fellowship}
        \item Explored and optimized probabilistic estimation algorithms.
        \item Authored a research paper on the probabilistic behavior of mathematical constants i.e Pi and e, integrating statistical analysis and computational methods.
        \item Awarded \$6,000 summer research preparatory fellowship.
\end{rSubsection}

    \begin{rSubsection}{\bf \href{https://github.com/ignasxv/master-of-education}{MathSafari Kits} – Math/Science Interactive Learning Hardware interface}
        {\ttfamily June 2024 - August 2024} 
        {Developer {\normalfont \small \ttfamily | ReactJS, NodeJS, Arduino, Socket.io, ExpressJS, TailwindCSS, Git \& github}} 
        {}
        \item Designed a hardware interface, integrating analogy sensors with a NodeJS backend and ReactJS frontend 
        \item Implemented serial communication for seamless hardware-software interaction, allowing students to experiment with variables and visualize results instantly.
        \item Enhanced team collaboration by developing virtual hardware using JavaScript and Arduino CLI, enabling remote development and testing without physical hardware.
        \item Accomplished real-time visualization of math and science concepts for intuitive learning, as measured by enhanced student engagement with interactive lessons.
    \end{rSubsection}

    \begin{rSubsection}
        {\bf Automatic Device for High Voltage Switching}
        {\ttfamily 2019 - 2022}
        {Microcontrollers Programming {\normalfont \small \ttfamily | C/C++ (Arduino), Circuit Design} }
        {}
        \item Designed and programmed an ESP32-based system to automate high voltage systems, specifically targeting remote areas with no IoT coverage.
        \item Integrated analog and digital sensors for monitoring electrical parameters, enabling real-time adjustments based on system load and conditions.
        \item Embedded GSM modules for remote communication and control, for areas with unreliable internet.
        \item Successfully deployed the system in 2 schools and churches, improving operational efficiency and reducing manual intervention.
    \end{rSubsection}

    % \begin{rSubsection}
    %     {\bf \href{https://techmasterevent.com/project/1andonly}{DigiCard Technologies} – Professional Contact Exchange Platform}
    %     {\ttfamily May 2023 - February 2024}
    %     {Startup Development {\normalfont \small \ttfamily | JavaScript, NFC Technology, Sanity, Headless CMS, Svelte \& Svelte-kit} }
    %     {}
    %     \item Implemented just-in-time client-side generation of contact cards, minimizing memory usage and backend load.
    %     \item Utilized ESP32 to create custom hardware for programming contact information into NFC cards
    %     \item Utilized spreadsheet as a backend for rapid development, enabling product launch within two weeks. Later, it migrated to a headless CMS- Sanity, allowing multiplatform data rendering.
    %     \item Secured distribution deals with three institutions, validating the platform’s viability and technical robustness.
    % \end{rSubsection}

    \begin{rSubsection}
        {\bf \href{https://pixel-hack.vercel.app/}{Pixel Hack} – Artistic Image Processing}
        {\ttfamily Aug 2023 - Present}
        {Image Processing {\normalfont \small \ttfamily | Python, JavaScript, NumPy} }
        {}
        \item Applied color quantization techniques using k-means clustering in Python to reduce the color palette, efficiently grouping colors while preserving key visual elements and optimizing the aesthetic appeal of the artwork.
        \item Developed an interactive web interface using JavaScript to visualize and explore the final artistic output in real-time.
        \item The final results were transformed into a physical sculpture and exhibited in a public library.
    \end{rSubsection}
    
    \begin{rSection}
        {}{}{}
    \end{rSection}
    

\end{rSection}
